\documentclass{CV}
\usepackage{hyperref}

\setname{Bruno}{Chicelli}
\setmail{rodriguessilvabruno@outlook.com}
\setposition{Data Scientist} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/brunorosilva/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/brunorosilva} %you can play with color of the template (red is also nice..)
\setmediumaccount{https://medium.com/@brunorosilva}
\setexternallink{https://brunorosilva.github.io/}

\setthemecolor{gray} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
%Sections
%
% Summary
\addblocktext{Summary}{
\explanationdetail{
Python\cpshalf SQL\cpshalf TensorFlow\cpshalf PyTorch\cpshalf LangChain\cpshalf PySpark\cpshalf Google Cloud Platform\cpshalf Amazon Web Services \\
\textbf{\emph{Fluent:}} English \cpshalf Portuguese \textbf{\emph{Proficient:}} Spanish \textbf{\emph{Beginner:}} German} \\
\textbf{Project \href{https://github.com/brunorosilva/img2art-search?tab=readme-ov-file}{Img2Art-Search}}. A Vision transformer model used to search for human art given any image}
    
%% Experience
\section{Professional Experience}
%
    \datedexperience{Handoff - Senior ML/AI Engineer - Austin (Remote)}{03/2025 - Current} 
    \explanationdetail{ 
    Creating the best AI to estimate construction costs.

        }\\
    \datedexperience{ReelGood - Senior Machine Learning Engineer - San Franscisco (Remote)}{11/2023 - 03/2025} 
    \explanationdetail{ 

    Responsible for a new version of the company core algorithm that matches movies, shows and shows episodes across 60+ streaming services in 8 languages, totaling more than 3 Million titles. Deployed it to AWS using Pytorch, ChromaDB, SBERT, Docker and AirFlow running on Kubernetes (EKS). The new solution improved upon the current one by 750x on performance, from 3s/title to 4ms/title with significantly better precision.
    }\\
    \datedexperience{Globo Group - Staff Machine Learning Engineer}{04/2023 - 11/2023} 
    \explanationdetail{ 
    Developed and deployed models and data pipelines to manage behavior graphs at a massive scale, serving a user base exceeding 100 million unique users. Using tech like Vertex AI, DataProc, DataFlow, and BigQuery on large-scale graphs. 
    \\
    
      Won the internal hackathon with user embeddings + generative AI to generate segment-optimized creatives and text for ads.}\\
    \datedexperience{Globo Group - Senior Data Scientist}{06/2021 - 03/2023} 
    \explanationdetail{ 
 Developed and deployed a real-time AI pipeline using PyTorch, TensorFlow, Python, OpenCV, AWS, Cloud Run and Functions which optimized ad placement in over 2k videos per day adding R\$10 million in revenue per year.
\\

 Developed a contextual extractor and clustering algorithm for every article published at G1, GShow and GE to assess the CTR lift provided by different contexts for advertisers. Used PyTorch, Top2Vec, Cloud Functions and Vertex AI;
\\

 Applied genetic algorithms to automate advertising strategies in broadcast and cable TV. This initiative yielded a remarkable annual revenue generation of over R\$30 million.

 }\\
    \datedexperience{Boa Vista Serviços - Data Scientist}{08/2020 - 06/2021} 
    \explanationdetail{ 
 
 Created a model for propensity of credit card acceptance and activation which was sold to a top20 world bank.
 \\

 Developed a faster ML pipeline reducing Data Scientists overhead from 2 weeks down to 3 hours using MLFlow and GCP;
     }\\    
    %
    \datedexperience{ArcelorMittal - Junior Data Scientist}{05/2019 - 07/2020} 
    \explanationdetail{ 
    Saved R\$1.3 million yearly with automation, machine learning and data science using Python, R, Azure, SQL;
    
    Created a sales forecasting project for over 100 points of sale all over Brazil.

     }     
    %
  
%Education
\section{Education}
    \datedexperience{USP - Polytechnic School of the University of São Paulo}{01/2020 - 12/2021} 
    \explanation{Artificial Intelligence Specialization} 
    \explanationdetail{ 
     2 year graduate studies in Machine Learning and Deep Learning - dissertation on YOLOv4 + SIFT for vehicle counting
    }
    \datedexperience{UFABC - Federal University of ABC}{05/2015 - 05/2019} 
    \explanation{Bachelors in Science and Technology} 
    \explanationdetail{ 
     Award of Merit in Physics III, top 75 student out of 1900 in the course - selected to teach other students
     }
%
\setlist[itemize]{leftmargin=*}

  %
%
% Experience
\section{Courses and Certificates}
    \newcommand{\extraevelven}{%
    \textbf{Data Science Dojo} - LLM Bootcamp working with RAG, LangChain, LangGraph, Vector DB (40 Hours) 
    }
    \newcommand{\extraone}{%
    \textbf{Google} - Advanced Solutions Lab (16 weeks focused on several tools for ML in GCP w/ Google Experts) 
    }
    \newcommand{\extratwo}{%
    \textbf{Deepmind.ai} - Deep Learning Specialization (16 weeks)
    }
    %
    \newcommand{\extrathree}{%
    \textbf{Deepmind.ai} - Tensorflow Developer Specialization (16 weeks) %replace this part with actual text
    }
    %
    \newcommand{\extrafive}{%
    \textbf{Deepmind.ai} - Machine Learning with Tensorflow in Google Cloud Platform (16 weeks) %replace this part with actual text
    }
    \newcommand{\extrasix}{%
    \textbf{Alura} (13 courses) Courses on Linux, Shell, Docker, Kubernetes and Flutter    }
    \newcommand{\extraeigth}{%
\textbf{Coursera} (16 courses) Machine Learning, Andew Ng and other 15 courses in the specializations    }
    \newcommand{\extraten}{%
\textbf{HarvardX} (3 courses) Data Science: Productivity Tools; Visualization; Machine Learning    }
    \newcommand{\extratwelve}{%
Volunteered in Buenos Aires, Argentina: taking care of children who lived in a orphanage in the suburbs, AIESEC    }

    \newcommand{\listofextras}{\extraevelven, \extraone, \extratwo, \extrathree,  \extrafive, \extrasix, \extraeigth, \extraten, \extratwelve}
    %
    \createbullets{\listofextras}
%
%Footnote
\end{document}
